\malg: a novel interest management algorithm for distributed simulations of MMOGs

### 2008-05-13 trunk/textos/dsrt/engaoi.tex
related work really done and spellchecked

The algorithms described in the following sections are mainly based on the euclidian distance between each avatar and all other entities in the virtual environment. This could create a scalability problem due to the processing of the distances, but a distributed architecture is assumed, where the processing can and should be parallelized. In the distribution model defined previously, each server controls a region of the map. Therefore, each one of them manages only a subset of the entities of the game, checking only the distances between each pair of them, in addition to the entities that are in a neighboring region, close to its border.

@@

The simplest way to execute interest management is to define a circular area, whose center is determined by the coordinates of the avatar's location in the virtual environment. After that, the euclidian distance between the avatar and every other entity in the game world is calculated. Let $A$ be an avatar, whose area of interest is a circle of radius $rad$. If an entity $E$ is at a distance less than $rad$ from $A$, then its state updates will be relevant to $A$. $A$ will not receive state updates from entities which are at a distance greater than $rad$. Figure \ref{fcirc} illustrates this type of area of interest.

>>>>

The algorithms described in the following sections are mainly based on the euclidean distance between each avatar and all other entities in the virtual environment. This could create a scalability problem due to the processing of the distances, but a distributed architecture is assumed, where the processing can and should be parallelized. In the distribution model defined previously, each server controls a region of the map. Therefore, each one of them manages only a subset of the entities of the game, checking only the distances between each pair of them, in addition to the entities that are in a neighboring region, close to its border.

@@

The simplest way to execute interest management is to define a circular area, whose center is determined by the coordinates of the avatar's location in the virtual environment. After that, the euclidean distance between the avatar and every other entity in the game world is calculated. Let $A$ be an avatar, whose area of interest is a circle of radius $rad$. If an entity $E$ is at a distance less than $rad$ from $A$, then its state updates will be relevant to $A$. $A$ will not receive state updates from entities which are at a distance greater than $rad$. Figure \ref{fcirc} illustrates this type of area of interest.
